draft_final_assignment

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

ggplot(daily_sentiment, aes(date, colour=partisan)) +
  geom_point(aes(y=score), size=0.5) + 
  geom_line(aes(y=score7)) + theme_minimal()
```

>>>>

ggplot(daily_sentiment, aes(x=date, y = score, colour=partisan)) +
  geom_point(aes(y=score), size=1) + 
  geom_line(aes(y=score7)) + theme_minimal() + geom_smooth(method = "lm")
```
